\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[margin=0.5in]{geometry}



\begin{document}
\begin{center}

\huge


\textbf{Yoga 100: Mastering Yoga}

\textbf{Fall 2018 Syllabus}


\end{center}

\noindent\rule[0.5ex]{\linewidth}{1pt}


\Large

\begin{flushleft}
\textbf{General information:}

\vspace{0.5cm}

\large

\underline{Student Team}:
\begin{itemize}[noitemsep,nolistsep]
    \item Lecturers: Shahen Mirzoyan, Vikash Raja, Jason Shi, Sophia Ding
\end{itemize}

\vspace{0.1cm}

\underline{Lectures}: Friday 3:00 PM - 5:00 PM, RSF Combatives

\vspace{0.1cm}

\underline{Prerequisites}: Ability to move and be open minded to painful stretches

\vspace{0.1cm}

\underline{Units}: 2

\vspace{0.1cm}

\underline{Grading}:
\vspace{0.1cm}
\begin{itemize}[noitemsep,nolistsep]
    \item 2 units. P/NP only. 70/100 points requires to pass the course
    \item Attendance counts towards roughly f55\% of overall grade
\end{itemize}


\vspace{0.1cm}

\underline{Permission numbers}: Will be distributed privately

\vspace{0.1cm}

\underline{Course Piazza}: https://piazza.com/berkeley/fall2018/yoga100/home

\vspace{0.1cm}

\underline{Attendance Policy}: 

\vspace{0.1cm}
\begin{itemize}[noitemsep,nolistsep]
    \item Attendance will be taken in class. Each day counts for 5 points.
\end{itemize}

\vspace{0.1cm}

\underline{Late Submission Policy}:
\begin{itemize}[noitemsep,nolistsep]
    \item 10\% of total assignment grade will be deducted for every day it is turned in late.
\end{itemize}

\vspace{0.1cm}

\underline{Academic Honesty}:

\vspace{0.1cm}
\begin{itemize}[noitemsep,nolistsep]
    \item Plagiarism will not be tolerated. Any evidence of cheating will result in immediate failure.
\end{itemize}


\noindent\rule[0.5ex]{\linewidth}{1pt}


\Large

\textbf{Course Overview}:



\large

Welcome to Yoga 100: Mastering Yoga! This course is created to help you learn, appreciate, and most importantly, master yoga. Our objective is to broaden your perspective on the benefits of yoga and to help you develop your flexibility.






\end{flushleft}












\end{document}
